An interactive environment for mapping computational structures to FPGAs

### 2016-07-07 paper/paper.tex
Described current state of SDFkit

  \todo[inline]{describe status of SDFkit}

>>>>

  Currently, SDFkit can import graphs expressed in a JSON file format.
  These files contain a list of nodes and edges.
  Additionally, each node contains a python lambda expression for the functional behavior of the node during simulation.
  After opening, both the functionality of the nodes and data on the edges can be altered using the GUI.
